---
title: "Quickstart Guide to the Fish Benefits Workbook"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quickstart Guide to the Fish Benefits Workbook}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette is intended for a very quick starting guide to using the app. 
It is not intended for a deep look at the steps in the Fish Benefits Workbook, and it doesn't discuss parameterization of the model. 
We assume that you have a template on hand, or can use the built-in template.

First, load the `fbwR` library.

```{r setup}
library(fbwR)
```

## Load the parameter template file

When you installed `fbwR`, it came with a template Excel file. 
You can identify the location of the file using the `system.file` function: 

```{r load_template}
template_location <- system.file(
  "extdata", "NONFINAL_template_data_entry_06012023.xlsx", package = "fbwR")

# Or
template <- fs::path_package("extdata", "NONFINAL_template_data_entry_06012023.xlsx", package = "fbwR")
```